### 2025-02-12 about/vita.tex
Updates for 2025

\begingroup\frenchspacing
\papercount=6
\pubbegin P
\papitem (with Jonah Saks)
On the homology of several number-theoretic set families.
{\sl Enumerative Combinatorics and Applications}\/ {4},2 (2024), \#S2R12, 11~pp.
[arXiv:2206.12535]
\papitem (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions.
{\sl Australasian Journal of Combinatorics}\/ {\bf 84},3 (2022), 357--374.
[arXiv:2106.05949]
\papitem (with Luc Devroye and Rosie Y. Zhao)
On the peel number and the leaf-height of a Galton--Watson tree.
{\sl Combinatorics, Probability and Computing}\/ {\bf 32},1 (2023), 68--90.
[arXiv:2106.14389]
\papitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl Discrete Mathematics
and Theoretical Computer Science}\/ {\bf 24},1 (2022), \#7, 16~pp.
[arXiv:2105.12046]
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. {\sl Random Structures and Algorithms}\/ {\bf 61},3 (2022), 520--542.
[arXiv:2007.05681]
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory}\/ {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]

@@

\fictioncount=4
\pubbegin F
\starficitem ``Lanterns,'' Winner of the 2024 Constance Rooke Creative Nonfiction Prize. To appear in
{\sl The Malahat Review}
\ficitem ``Senang Diri,'' {\sl Existere} {\bf 42},2 (2023), 17--25.
\ficitem ``The Vigil,'' {\sl Ricepaper Magazine} (2023), online. Reprinted in
{\sl Best Canadian Stories 2025} (Windsor, Ont.: Biblioasis, 2024), 244--253.
\ficitem ``Mountain Pass,'' {\sl Prairie Journal of Canadian Literature} {\bf 79} (2023), 48--55.
\endgroup%end the frenchspacing

@@

\leftright{\bf DRP Mentor}{\bf January 2022 -- April 2024}
\leftright{\sl Department of Mathematics and Statistics, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Met with two undergraduate students as part of the Directed Reading Program
on a weekly basis to give them an introduction to research-level
mathematics in a casual setting. Focused on topics in extremal combinatorics related to the increasing
triples problem, as well as topics related to Khovanskii's theorem.
\medbreak

@@

\starleftright{\bf Software developer}{\bf January -- May 2023}
\leftright{\sl Levven}{\sl Edmonton, AB, Canada}
\smallskip
Developed firmware for the manufacture and function of in-home IoT gateways, smart switches,
and related electronic products. Code primarily in \CEE\ and Python. Contributed to the open-source
Mongoose OS codebase.
\medbreak

\starleftright{\bf Visiting teaching assistant}{\bf July 2022}
\leftright{\sl Bocconi University}{\sl Como, CO, Italy}
\smallskip
Teaching assistant for a two-week summer school on random structures and combinatorial statistics,
which was
organised by Bocconi University in collaboration with Oxford University
and Imperial College London. Led problem sessions in the afternoons, with
around forty graduate-level students were in attendance.
\medbreak

@@

\starleftright{\bf Grader}{\bf September 2019 -- April 2021}
\leftright{\sl Department of Mathematics and Statistics, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Grading of assignments in the following courses:
\begingroup\parindent=10pt
\smallskip
\thing Winter 2021: MATH 457 Honours Algebra 4
\smallskip
\thing Fall 2020: MATH 323 Probability, MATH 456 Honours Algebra 3
\smallskip
\thing Winter 2020: MATH 240 Discrete Structures
\smallskip
\thing Fall 2019: MATH 235 Algebra 1
\endgroup
\medbreak

@@

\leftright{\bf Vice President, Academic}{\bf May 2019 -- January 2020}
\leftright{\sl Society of Undergraduate Mathematics Students}{\sl Montr\'eal, QC, Canada}
\smallskip
Oversaw academic affairs within SUMS council and acted as liaison between the undergraduate community and
mathematics faculty. Duties included representing the student body at department meetings,
organising midterm and final review sessions,
and helping students with
academic concerns.
\medbreak

>>>>

\begingroup\frenchspacing
\papercount=6
\pubbegin P
\papitem (with Jonah Saks)
On the homology of several number-theoretic set families.
{\sl Enumerative Combinatorics and Applications}\/ {\bf 4},2 (2024), \#S2R12, 11~pp.
[arXiv:2206.12535]
\papitem (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions.
{\sl Australasian Journal of Combinatorics}\/ {\bf 84},3 (2022), 357--374.
[arXiv:2106.05949]
\papitem (with Luc Devroye and Rosie Y. Zhao)
On the peel number and the leaf-height of a Galton--Watson tree.
{\sl Combinatorics, Probability and Computing}\/ {\bf 32},1 (2023), 68--90.
[arXiv:2106.14389]
\papitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl Discrete Mathematics
and Theoretical Computer Science}\/ {\bf 24},1 (2022), \#7, 16~pp.
[arXiv:2105.12046]
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. {\sl Random Structures and Algorithms}\/ {\bf 61},3 (2022), 520--542.
[arXiv:2007.05681]
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory}\/ {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]

@@

\fictioncount=4
\pubbegin F
\starficitem ``Lanterns,'' {\sl The Malahat Review} {\bf 229} (2025), 7--13.
Winner of the 2024 Constance Rooke Creative Nonfiction Prize.
\ficitem ``Senang Diri,'' {\sl Existere} {\bf 42},2 (2023), 17--25.
\ficitem ``The Vigil,'' {\sl Ricepaper Magazine} (2023), online. Reprinted in
{\sl Best Canadian Stories 2025} (Windsor, Ont.: Biblioasis, 2024), 244--253.
\ficitem ``Mountain Pass,'' {\sl Prairie Journal of Canadian Literature} {\bf 79} (2023), 48--55.
\endgroup%end the frenchspacing

@@

\leftright{\bf DRP Mentor}{\bf January 2022 -- April 2024}
\leftright{\sl Department of Mathematics and Statistics, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Met with undergraduate students as part of the Directed Reading Program
on a weekly basis to give them an introduction to research-level
mathematics in a casual setting.
\begingroup\parindent=10pt
\smallskip
\thing Winter 2024: Topics in additive combinatorics, with a particular focus on Roth's theorem.
\smallskip
\thing Winter 2022: Topics in extremal combinatorics related to the increasing
triples problem, as well as topics related to Khovanskii's theorem.
\endgroup
\medbreak

@@

\starleftright{\bf Software developer}{\bf January -- May 2023}
\leftright{\sl Levven}{\sl Edmonton, AB, Canada}
\smallskip
Developed firmware for the manufacture and function of in-home IoT gateways, smart switches,
and related electronic products. Worked primarily in \CEE\ and Python. Contributed to the open-source
Mongoose OS codebase.
\medbreak

\starleftright{\bf Visiting teaching assistant}{\bf July 2022}
\leftright{\sl Bocconi University}{\sl Como, CO, Italy}
\smallskip
Teaching assistant for a two-week summer school on random structures and combinatorial statistics,
which was
organised by Bocconi University in collaboration with Oxford University
and Imperial College London. Led problem sessions in the afternoons, with
around forty graduate-level students in attendance.
\medbreak

@@

\starleftright{\bf Grader}{\bf September 2019 -- April 2021}
\leftright{\sl Department of Mathematics and Statistics, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Graded assignments in the following courses:
\begingroup\parindent=10pt
\smallskip
\thing Winter 2021: MATH 457 Honours Algebra 4
\smallskip
\thing Fall 2020: MATH 323 Probability, MATH 456 Honours Algebra 3
\smallskip
\thing Winter 2020: MATH 240 Discrete Structures
\smallskip
\thing Fall 2019: MATH 235 Algebra 1
\endgroup
\medbreak

@@

\leftright{\bf Vice President, Academic}{\bf May 2019 -- January 2020}
\leftright{\sl Society of Undergraduate Mathematics Students}{\sl Montr\'eal, QC, Canada}
\smallskip
Oversaw academic affairs within {\mc SUMS} council and acted as liaison between the undergraduate community and
mathematics faculty. Duties included representing the student body at department meetings,
organising midterm and final review sessions,
and helping students with
academic concerns.
\medbreak
